\documentclass[../main.tex]{subfiles}

\begin{document}
\section{Beautification of Images by Generative Adversarial Networks (GANs)}
%%%% General introduction
For millennia, philosophers have been arguing about the nature of beauty. Yet after all these years, we still can't confidently claim to understand what beauty even \textit{is}. Furthermore, the fundamental question whether beauty is subjective or objective remains unsettled \parencite{sep-beauty}. In this paper, we will use state-of-the-art machine learning techniques to try and create a so-called `visual definition' of beauty.


%%%% Philosophy
\subsection{Defining Beauty}
% What is beauty?
Throughout history, there have been different conceptions of beauty. The classical conception of beauty, often embodied in classical art, typically concerns the arrangement of independent parts into a coherent whole through properties such as symmetry and order \parencite{wolfflin1932principles, sep-beauty}. Another important conception is the idealist conception of beauty described by Plato as a perfect unity. This is in contrast to the classical conception which emphasizes individual parts \parencite{sep-beauty}. 18th century empiricist philosophers on the other hand looked at beauty in a more instrumental, hedonistic sense. \textcite{hume2003treatise} for example argues that beauty exists to give pleasure and satisfaction to the soul.

% Subjectivity and objectivity
While most classical philosophers would have argued that beauty is a property of an object that exists outside the mind, Renaissance and later philosophers argue more for a combination of some objective properties with unique subjective appreciations \parencite{sartwell2017entanglements}. The assumption that there are indeed some objective properties to beauty allows us to examine what exactly it means for something to be beautiful.

% Philosophy of aesthetics



%%%% Psychology
\subsection{How we Perceive Beauty}
% Transition to psychology
The shift from a pure objective conception of beauty towards a more nuanced combination of objective properties with subjective perception preceded the start of psychology as an empirical science in the 19th century. Among these early psychologists a school of thought known as Gestalt psychology came to fruition in the early 20th century. The Gestalt psychologists created a framework of visual perception that emphasizes patterns and configurations of objects rather than individual components \parencite{wagemansCenturyGestaltPsychology2012a}. Examples of perceptual grouping principles are proximity, similarity, continuity, closure, and connectedness \parencite{goldstein2009perceiving}. In the Gestalt framework, principles such as these are the building blocks for our visual system \parencite{wagemansCenturyGestaltPsychology2012a}.

% Studies on aesthetics
Later psychological research focusing on art and aesthetic appreciation has found that there are  certain principles that tend to evoke a certain aesthetic quality across cultures such as for example symmetry \parencite{bodeCrossculturalComparisonPreference2017}, order and complexity \parencite{van2021order}, and figure-ground contrast \parencite{reberProcessingFluencyAesthetic2004}. Mirroring the progression in philosophy, modern views on aesthetics from neuroscience and experimental psychology support an interactionist interpretation of beauty: objects do contain intrinsic properties conveying beauty, but the final aesthetic appraisal comes from an interaction between these objective properties and a subjective observer \parencite{valenziseAdvancesChallengesComputational2022}.

% Processing fluency
One influential framework that incorporates the interactionist interpretation of beauty is that of processing fluency formulated by \textcite{reberProcessingFluencyAesthetic2004}. In this framework, the aesthetic experience is determined by the fluency with which a perceived object is processed. Processing fluency relies on an interaction of objective properties such as the principles from Gestalt psychology with subjective factors such as personal experiences and expectations.
% Evolutionary psychology
% Supernormal stimuli??
% Hyperreality
% Peak shift principle
% Refer to AestheticsNet



\subsection{Machine Learning and Beauty}
% Introduce Computational Aesthetics
One of the biggest technological advances in recent years is in the field of machine learning. This `Deep Learning Revolution' was sparked by the continuous efforts of researchers and engineers, the increasing availability of big data, and the boost in computing power \parencite{sejnowskiDeepLearningRevolution2018}. Because these networks have some organizational similarities to the human brain, they can potentially be used as a means to study obscure mental representations in humans \parencite{guoDeepLearningVisual2016, goetschalckx2021generative}. 

Computational aesthetics is defined as the research of human aesthetic decision making through computational methods \parencite{valenziseAdvancesChallengesComputational2022, hoenig2005proceedings}. As a result of the deep learning revolution, more and more types of artificial neural networks have become available to be used as a means to study human aesthetic behavior.

% Introduction to GANs
Generative Adversarial Networks (GANs) are a relatively recent development characterized by two competing neural networks \parencite{goodfellow2014generative}. The first network, the generator, starts generating random outputs and the second network, the discriminator, receives inputs from the generator and compares these to a real dataset \parencite{creswellGenerativeAdversarialNetworks2018}. In the context of image generation, the inputs and outputs are images. Importantly, the discriminator has been trained on a real dataset and will judge the output generated by the generator. The generator receives the feedback and over many iterations will slowly learn to create better outputs that start to resemble the real dataset the discriminator had been trained on. Both the generator and the discriminator improve over time and as a result, the generator will be able to generate more convincing outputs and the discriminator will be able to differentiate much better between real and fake.

% Use of GANs in cognitive science

% GANalyze to obtain a visual definition
\textcite{goetschalckxGANalyzeVisualDefinitions2019} have developed GANalyze, a framework using GANs that allows us to study cognitive properties by means of so-called visual definitions. In their paper, \textcite{goetschalckxGANalyzeVisualDefinitions2019} utilized their network to generate images of varying levels of memorability which were validated in a behavioral task. GANalyze makes this possible by using as the discriminator a convolutional neural network (CNN) designed for predicting image memorability \parencite{khosla2015understanding}.



%%%% Theoretical framing of the research problem
\subsection{Present Study}
The goal of this study is to investigate the factors underlying the aesthetic value of images using GANalyze. We will use GANalyze to generate sequences of images that we hypothesize possess either \textit{more}, or \textit{less} aesthetic quality depending on the internal variable used for their respective generations. By comparing the low-aesthetic images to the high-aesthetic images, we will be able to examine the underlying factors responsible for making an image either more or less beautiful. We will also perform a finer analysis of the aesthetics-related parameters by looking into the hidden layers of the trained GANalyze network.

% AestheticNet & BigGAN potentially

% GANalyze validation
However, if we wish to learn something about human aesthetics appraisal from a GAN, we must first validate whether the GAN truly `understands' what it means for an image to possess aesthetic quality. To do so, we will validate whether human participants tend to agree with GANalyze on which image appears to be more beautiful. We are also interested whether a person's experience with art and their demographic characteristics affect their proportion of agreement with the GAN. A relation between art experience and agreement with the GAN could have important implications for the validation of the network and the generalizability of the final results.


\end{document}